Paradigms in Physics 2.0

### 2017-06-29 paper.tex

\begin{abstract}
In 2016, the Department of Physics at Oregon State University began a
process to revise our Paradigms in Physics curriculum for physics
majors.  This paper will describe both the process by which our
department achieved consensus on this curricular change, and the
resulting curriculum.  The Paradigms 2.0 committee begain with a
survey of students and faculty, followed by individual interviews with
the faculty teaching each existing course.  As we developed a plan to
address student- and faculty-identified challenges in the curriculum,
we met with each faculty member individually to explain and refine our
proposal, which was unanimously approved by the faculty.  Major
changes include major changes to several courses (math
methods, computational physics, modern physics, electronics, and
classical mechanics), including the introduction of two sophomore-year
courses designed specifically to help prepare students to for their
upper-division courses.
\end{abstract}

\maketitle
% * <ethan.minot@oregonstate.edu> 2017-06-28T19:21:10.109Z:
%
% ^.
\section{Introduction}
The Paradigms in Physics program is a rethinking of the upper-division
The Paradigms in Physics project began in 1996, when three faculty
members at Oregon State applied to the NSF for funding to redesign the
upper-division curriculum.  The motivation for the original Paradigms
project was in fact similar to the motivation for Paradigms 2.0: a
desire to soften the ``brick wall'' encountered by students upon
reaching the junior year, within the constraint that transfer students
must be able to graduate with two years of upper-division
courses~\cite{manogue2001paradigms}.  On top of this, there was a
desire to provide students with a broad knowledge of physics prior to
the GRE exams in the fall of their senior year.  The process of
redesigning the curriculum was dominated by the creation of index cards
listing subject content, and sorting these cards into courses.  This
process involved the entire faculty, and culminated in a unanimous
agreement to adopt the resulting curriculum.

The resulting curriculum was primarily composed of junior-year
``Paradigms'' courses, followed by senior-year ``Capstone'' courses.
The Paradigms were intensive 2-credit, 3-week courses which meet every
day, for a total of seven hours per week.  Paradigms incorporate
laboratory experiences and active engagement into the class, and
typically have two problem sets per week.  Capstones were more
traditional 3-credit courses which meet three hours per week for an
entire quarter.  The Paradigms courses had integrated math content,
followed by a Math Methods course.

Two decades have passed since the original Paradigms effort.
During this time we have made a number of changes: e.g. a new
\emph{first} Paradigm was introduced to soften the beginning of the
junior year, the order of Paradigms was shuffled more than once, Math
Methods was moved from the beginning of the senior year to the end of
the junior year, and a computational laboratory course was introduced
to accompany the Paradigms.  The faculty maintained the tradition of meeting
every three weeks to discuss issues relating to upper-division
teaching.  New faculty arrived and learned to teach the new courses,
and introduced their own ideas to the courses.

\subsection{Motivation for Paradigms 2.0}
There were a number of factors that motivated us to embark on the
Paradigms~2.0 process.  In the last two decades, we have observed
a number of challenges students face in the Paradigms.  While in many cases we
addressed these by changing and reordering the courses, we felt a look
at the entire curriculum was in order.  In addition, our faculty
understanding of the details of the sequence was diminishing by attrition: 
while our younger
faculty are enthusiastic about the Paradigms, many lack perspective on
where students are in a given course, and what content is essential
for students to grasp prior to a following course.

@@

% David R, Ethan, Oksana, Bo, Guenter, Weihong, Matt, Yun-Shik, Heidi,
% Liz, Davide = 11
Only 5 of our 16 current tenure-line faculty were involved in the
orignal Paradigms effort.  Some of the newest faculty have only a
superficial understanding of our course structure.  This poses a
challenge when these professors teach courses that are closely
intertwined with one another.

\section{Paradigms 2.0 process}
We began the Paradigms 2.0 process in the Winter of 2016, having in
the previous year obtained faculty agreement, and support from our
Department head.  The process was spearheaded by a committee of four
(the authors DR, EG, EM, and CAM, with EvZ present at meetings
documenting our process).  During the Winter quarter, we informed the
community of our process through a colloquium, and collected student
and faculty perspectives on the existing curriculum.  We then
interviewed faculty who recently taught each of our existing courses
to document topics that were currently covered.  This resulted in a
total of $\sim$700 index cards in $\sim$30 stacks, with each stack
corresponding to one course, and each card describing a topic,
color-coded as in Fig.~\ref{fig:schedule}.

@@

\section{Changes made}
As a result of this process, we have implemented a number of changes
to our physics major curriculum.  The resulting curriculum is outlined
in Fig.~\ref{fig:schedule}.  The changes consisted of introducing two
new sophomore-level courses (which may be taken in the junior year) to
better prepare our majors for the Paradigms.  We eliminated Modern
Physics and the Classical Mechanics capstone in favor of the two new
sophomore-level courses.  We eliminated the Math Methods course in
favor of ``math bits'' integrated into the Paradigms themselves.
Finally, we restructured our nine 3-week Paradigms courses into six
5-week Paradigms.  We changed our computational physics requirement,
and reduced the number of electronics courses.

\subsection{5-week Paradigms}
To begin with the most distinctive feature of our curriculum, we
wanted to maintain the existing intensive 7-hour-per-week schedule in
the junior year, which we have found effective.  However, we chose to
change from three 3-week Paradigms per quarter to two 5-week Paradigms
per quarter.    This change has several advantages.  It gives students
a bit more time with each professor prior to their final exam.  This
gives a bit more flexibility, for instance, in case of illness.
Finally, by reducing the number of Paradigms, we allow the curriculum
to be taught with fewer faculty, albeit at an increased work load per professor.

We put considerable thought into the content and ordering of the new
Paradigms.  In most cases, we think of each 5-week Paradigm as either
one formerly 4-week Paradigm (the one that consumed the extra week
each quarter), two 3-week Paradigms compressed, or three 3-week paradigms combined into two 5-week paradigms.  The major
scheduling change is to place Static Fields (electrostatics and
magnetostatics) in the spring quarter.  
This intended to give students, especially transfer students, 
a bit more time to take Vector Calculus.  It also puts all use of
curvilinear coordinates in the spring quarter, which should ease the
learning of Central Forces.  The final major change was to move special relativity from the junior-year Paradigms to the new sophomore-level Theoretical Mechanics course.

\subsection{Math bits}
We chose to eliminate the Math Methods course in favor of formal
``math bits'' in the Paradigms.  Our previous Math Methods Capstone
posed a challenge regarding placement in the curriculum: it needed to
be sufficiently late for students to be adequately prepared
for advanced mathematical content, but in order to be functional in
the curriculum it should teach content that is required by other
physics courses, and thus should be earlier in the curriculum.  In
response to these issues, and in recognition that the majority of our
majors are not bound for graduate school, and have no need for
advanced math methods, we chose to integrate the needed math content
into the Paradigms, and allow advanced students to take our
graduate-level Math Methods course.  In order to ensure that our
students to receive the math instruction they require, and based on
our previous experience with math-intensive weeks (the \davidsays{``extra''
weeks having 3-week courses fitted into a 10-week quarter})
in the Paradigms, we chose to integrate one week of ``math bits'' into
each Paradigm.  The math bits for the entire year are treated as a
distinct teaching assignment, so students will be accustomed to the
treatment of math as a distinct subject supporting the physics
content.  This provides some relief from teaching for the Paradigms
professors, and at the same time ensures that they do not succumb to
the temptation to short-change the math content to the detriment of
the students.
\corinnesays{This paragraph is awkward.  I'm still thinking about some rewording.  This might be a good paragraph to discuss this afternoon.}

\subsection{Electronics}
We chose to reduce the Electronics requirement from two 3-credit
courses to one 3-credit course.  For many physics majors, this is more
than sufficient, and gives students a greater number of electives.  In
addition, we removed the lecture section of this course---which had
developed an unusually high student work load for a 3-credit
course---in favor of in-lab instruction.

A final change to Electronics is that we now will \emph{require}
Electronics during the junior year (specifically as a prerequisite for
the Oscillations and Waves Paradigm).  This is made possible by the reduction in
Fall workload for incoming transfer students, who had previously
usually taken Electronics as a senior.  This change has enabled us to
articulate distinct and sequenced learning outcomes from these two
courses, particularly in the realm of complex exponentials and Fourier
transforms.  It is also beneficial in providing students with
trouble-shooting skills prior to the in-class labs taught in
Oscillations and Waves course.

\subsection{Computational lab}
Over the last six years, we have been developing a 1-credit
computational laboratory course that accompanies the Paradigms.  We
chose to require this course, while removing a requirement for a
lower-division 3-credit course in computational physics.  This
lower-division course was challenging to teach, since it always had a
mix of lower- and upper-division students, with very different skill
levels and needs.  Transfer students now take computation alongside
the non-transfer students. The course is taught in a laboratory setting using pair
programming to help new programmers to learn.

\subsection{Sophomore courses}
We introduced two new sophomore-level courses: \emph{Physics of
Contemporary Challenges} and \emph{Techniques of Theoretical Mechanics}.  Both of
these courses ramp up student mathematical abilities prior to their
junior year.  The Challenges course focuses on estimation,
dimensional reasoning, and interpretation of integrals, while
Theoretical Mechanics teaches power series approximations and
exposes students to increased levels of mathematical sophistication.

These courses have the challenge (which was removed from
the computational course!)\corinnesays{remove this parenthetical comment} 
of teaching both juniors and sophomores
together.  They are taught in the winter and spring quarters, so
as to reduce the burden on transfer students in the Fall.  They were
explicitly constructed to \emph{not} teach any content required for
Fall or Winter Paradigms so that they can be taken concurrently with
the Paradigms.

\subsubsection{Challenges in Contemporary Physics}
\corinnesays{You might want to use your paragraph structure here, rather than sub-sub sections.}

In ``The Physics of Contemporary Challenges'' we prepare students to
apply physics concepts and physical reasoning skills to sustainable
energy issues, climate change mechanisms, space exploration and
puzzles in fundamental physics. These ``real-world'' topics are chosen
for either the societal need (energy and climate), and/or the human
need to explore (space and fundamental physics). By prioritizing
inclusion of the most engaging challenges, we aim to attract and
retain as many potential physics majors as possible.

@@

While the Challenges course takes a more experimental/applied physics
focus, the Methods of Theoretical Mechanics course has a more
theoretical physics flavor. The theme of this course is the discussion
of strategies for making sense of physics problems and symbolic
problem solving. This sense-making includes coordinating and
interpreting symbolic expressions with conceptual understandings,
geometric relationships, and physical intuitions.

The Theoretical Mechanics course is aimed at students who are taking
or have completed the last course in the introductory sequence. The
physics content of the course is advanced Newtonian mechanics,
introduction to Lagrangian and Hamiltonian techniques, and special
relativity. These topics at this stage for the students are convenient
for explicit discussion of sense-making strategies in physics because
(a) students are have recently studied problems that serve as limiting
cases for these more complex problems, (b) students at this level are
transitioning from solving problems primarily involving numbers to
problems with only symbolic parameters, and (c) sense-making as strategies 
can be discussed for approaching a problem, evaluating
answers, and refining intuitions about relativistic and other
unfamiliar situations. For example, we teach students how to use
spacetime diagrams to develop a story about a relativistic situation
and how to use hyperbola trigonometry on these diagrams to perform Lorentz
transformations that can be checked against the results of algebraic
Lorentz transformations.  The sense-making goals of the course are on
an equal footing with the physics goals, and sense-making is integrated
explicitly in all aspects of the course: exams, homework and during
in-class activities. Our aim is that students will develop
sense-making skills that will improve their learning in advanced
courses and will be valued by their upper-division course instructors,
research advisors, and future employers.

@@

\section{Summary}
We have developed a significant change to the Paradigms
curriculum.  This change focuses on the first two big ideas underlying
the Paradigms: (1) close attention to content ordering, and (2)
developing a consensus and understanding of the curriculum among our
faculty members.  Our commitment to using active engagement in our
upper-division curriculum remains unchanged.  While the specific
content ordering we developed may be interesting, the \emph{process} by
which we reached it and developed a faculty consensus is at the
essence of what makes the Paradigms in Physics program distinctive.
Emily van Zee, a researcher with experience in ..., 
\corinnesays{Emily, please add a short description of yourself} 
has completed a retrospective study of the process we used to develop the 
original Paradigms program and we have used her results extensively in 
designing and implementing the Paradigms 2.0 process.  She has continued 
to observe, study, and document our work as we have begun implementing 
the revised curriculum. 
\corinnesays{David:  Add a citation to http://physics.oregonstate.edu/portfolioswiki/toolkit:start}
The process of developing faculty understanding of the Paradigms is
ongoing, as we are having professors new to the Paradigms shadow
experienced faculty as they teach in the Paradigms, prior to teaching
the courses themselves.

>>>>

\begin{abstract}
In 2016, the Department of Physics at Oregon State University began a
process to revise our Paradigms in Physics curriculum for physics
majors.  This paper will describe both the process by which our
department achieved consensus on this curricular change, and the
resulting curriculum.  The Paradigms 2.0 committee began with a
survey of students and faculty, followed by individual interviews with
the faculty teaching each existing course.  As we developed a plan to
address student- and faculty-identified challenges in the curriculum,
we met with each faculty member individually to explain and refine our
proposal, which was unanimously approved by the faculty.  Major
changes include major changes to several courses (math
methods, computational physics, modern physics, electronics, and
classical mechanics), including the introduction of two sophomore-year
courses designed specifically to help prepare students to for their
upper-division courses.
\end{abstract}

\maketitle
% * <ethan.minot@oregonstate.edu> 2017-06-28T19:21:10.109Z:
%
% ^.
\section{Introduction}
The Paradigms in Physics project began in 1996, when three faculty
members at Oregon State applied to the NSF for funding to redesign the
upper-division curriculum.  The motivation for the original Paradigms~1.0
project was in fact similar to the motivation for Paradigms~2.0: a
desire to soften the ``brick wall'' encountered by students upon
reaching the junior year, within the constraint that transfer students
must be able to graduate with two years of upper-division
courses~\cite{manogue2001paradigms}.  On top of this, there was a
desire to provide students with a broad knowledge of physics prior to
the GRE exams in the fall of their senior year.  The process of
redesigning the curriculum was dominated by the creation of index cards
listing subject content, and sorting these cards into courses.  This
process involved the entire faculty, and culminated in a unanimous
agreement to adopt the resulting curriculum.

The resulting curriculum was primarily composed of intensive junior-year \emph{Paradigm}
courses, followed by more conventional senior-year courses.
The \emph{Paradigm} courses meet every day for a total of seven
hours per week for 3 weeks.  These courses incorporate
laboratory experiences and active engagement into the class, and
typically have two problem sets per week.  These courses also had
integrated math content, and were followed by a \emph{Math Methods} course.
The senior-year courses are more traditional 3-credit courses which meet
three hours per week for an entire quarter.

Two decades have passed since the original Paradigms~1.0 effort.
During this time we have made a number of changes: e.g. a new
first \emph{Paradigm} course was introduced to soften the beginning of the
junior year, the order of courses was shuffled more than once, \emph{Math
Methods} was moved from the beginning of the senior year to the end of
the junior year, and a computational laboratory course was introduced
to accompany the junior-year \emph{Paradigm} courses.  The faculty maintained the tradition of meeting
every three weeks to discuss issues relating to upper-division
teaching.  New faculty arrived and learned to teach the new courses,
and introduced their own ideas to the courses.

\subsection{Motivation for Paradigms 2.0}
There were a number of factors that motivated us to embark on the
Paradigms~2.0 process.  In the last two decades, we have observed
a number of challenges students face in our major.  While in many cases we
addressed these by changing and reordering the courses, we felt a look
at the entire curriculum was in order.  In addition, our faculty
understanding of the details of the sequence was diminishing by attrition: 
while our younger
faculty are enthusiastic about the Paradigms program, many lack perspective on
where students are in a given course, and what content is essential
for students to grasp prior to a following course.

@@

% David R, Ethan, Oksana, Bo, Guenter, Weihong, Matt, Yun-Shik, Heidi,
% Liz, Davide = 11
Only 5 of our 16 current tenure-line faculty were involved in the
orignal Paradigms~1.0 effort.  Some of the newest faculty have only a
superficial understanding of our course structure.  This poses a
challenge when these professors teach courses that are closely
intertwined with one another.

\section{Paradigms 2.0 process}
We began the Paradigms~2.0 process in the Winter of 2016, having in
the previous year obtained faculty agreement, and support from our
Department head.  The process was spearheaded by a committee of four
(the authors DR, EG, EM, and CAM, with EvZ present at meetings
documenting our process).  During the Winter quarter, we informed the
community of our process through a colloquium, and collected student
and faculty perspectives on the existing curriculum.  We then
interviewed faculty who recently taught each of our existing courses
to document topics that were currently covered.  This resulted in a
total of $\sim$700 index cards in $\sim$30 stacks, with each stack
corresponding to one course, and each card describing a topic,
color-coded as in Fig.~\ref{fig:schedule}.

@@

\section{Changes made}
As a result of this process, we have implemented a number of changes
to our physics major curriculum.  The resulting curriculum is outlined
in Fig.~\ref{fig:schedule}.  The changes consisted of introducing two
new sophomore-level courses (which may be taken in the junior year) to
better prepare our majors for the their junior year.  We eliminated \emph{Modern
Physics} and the \emph{Classical Mechanics Capstone} in favor of the two new
sophomore-level courses.  We eliminated the \emph{Math Methods} course in
favor of ``\emph{Math Bits}'' integrated into the \emph{Paradigm} courses.
Finally, we restructured our nine 3-week \emph{Paradigm} courses into six
5-week \emph{Paradigm} courses.  We changed our computational physics requirement,
and reduced the number of electronics courses.

\subsection{5-week \emph{Paradigm} courses}
To begin with the most distinctive feature of our curriculum, we
wanted to maintain the existing intensive 7-hour-per-week schedule in
the junior year, which we have found effective.  However, we chose to
change from three 3-week courses per quarter to two 5-week courses
per quarter.    This change has several advantages.  It gives students
a bit more time with each professor prior to their final exam.  This
gives a bit more flexibility, for instance, in case of illness.
Finally, by reducing the number of courses, we allow the curriculum
to be taught with fewer faculty, albeit at an increased work load per professor.

We put considerable thought into the content and ordering of the new
courses.  In most cases, we think of each 5-week \emph{Paradigm} course as either
one formerly 4-week \emph{Paradigm} course (the one that consumed the extra week
each quarter), two 3-week courses compressed, or three 3-week courses combined
into two 5-week paradigms.  The major
scheduling change is to place \emph{Static Fields} (electrostatics and
magnetostatics) in the spring quarter.  
This gives students, especially transfer students, 
a bit more time to take \emph{Vector Calculus}.  It also puts all use of
curvilinear coordinates in the spring quarter, which should ease the
learning of \emph{Central Forces}.  The final major change was to move
special relativity from the junior year to the new sophomore-level
\emph{Theoretical Mechanics} course.

\subsection{Math bits}
We chose to eliminate the \emph{Math Methods} course in favor of formal
\emph{Math Bits} in the \emph{Paradigm} courses.  Our previous \emph{Math Methods} course
posed a challenge regarding placement in the curriculum: it needed to
be sufficiently late for students to be adequately prepared
for advanced mathematical content, but in order to be functional in
the curriculum it should teach content that is required by other
physics courses, and thus should be earlier in the curriculum.  In
response to these issues, and in recognition that the majority of our
majors are not bound for graduate school, and have no need for
advanced math methods, we chose to integrate the needed math content
into the \emph{Paradigm} courses, and allow advanced students to take our
graduate-level \emph{Math Methods} course.  In order to ensure that our
students to receive the math instruction they require, and based on
our previous experience with math-intensive weeks (the \davidsays{``extra''
weeks having 3-week courses fitted into a 10-week quarter})
in the \emph{Paradigm} courses, we chose to integrate one week of \emph{Math Bits} into
each \emph{Paradigm} course.  The \emph{Math Bits} for the entire year are treated as a
distinct teaching assignment, so students will be accustomed to the
treatment of math as a distinct subject supporting the physics
content.  This provides some relief from teaching for
professors teaching \emph{Paradigm} courses, and at the same time ensures
that they do not succumb to the temptation to short-change the math content
to the detriment of the students.
\corinnesays{This paragraph is awkward.  I'm still thinking about some rewording.  This might be a good paragraph to discuss this afternoon.}

\subsection{Electronics}
We chose to reduce the \emph{Electronics} requirement from two 3-credit
courses to one 3-credit course.  For many physics majors, this is more
than sufficient, and gives students a greater number of electives.  In
addition, we removed the lecture section of this course---which had
developed an unusually high student work load for a 3-credit
course---in favor of in-lab instruction.

A final change to Electronics is that we now will \emph{require}
\emph{Electronics} during the junior year (specifically as a prerequisite for
\emph{Oscillations and Waves}).  This is made possible by the reduction in
Fall workload for incoming transfer students, who had previously
usually taken \emph{Electronics} as a senior.  This change has enabled us to
articulate distinct and sequenced learning outcomes from these two
courses, particularly in the realm of complex exponentials and Fourier
transforms.  It is also beneficial in providing students with
trouble-shooting skills prior to the in-class labs taught in
\emph{Oscillations and Waves}.

\subsection{Computational lab}
Over the last six years, we have been developing a 1-credit
computational laboratory course that accompanies the \emph{Paradigm} courses.  We
chose to require this course, while removing a requirement for a
lower-division 3-credit course in computational physics.  This
lower-division course was challenging to teach, since it always had a
mix of lower- and upper-division students, with very different skill
levels and needs.  Transfer students now take computation alongside
the non-transfer students. The course is taught in a laboratory setting using pair
programming to help new programmers to learn.

\subsection{Sophomore courses}
We introduced two new sophomore-level courses: \emph{Physics of
Contemporary Challenges} and \emph{Techniques of Theoretical Mechanics}.  Both of
these courses ramp up student mathematical abilities prior to their
junior year.  The \emph{Challenges} course focuses on estimation,
dimensional reasoning, and interpretation of integrals, while
\emph{Theoretical Mechanics} teaches power series approximations and
exposes students to increased levels of mathematical sophistication.

These courses have the challenge of teaching both juniors and sophomores
together.  They are taught in the winter and spring quarters, so
as to reduce the burden on transfer students in the Fall.  They were
explicitly constructed to \emph{not} teach any content required for
Fall or Winter junior-year courses so that they can be taken concurrently with
those courses.

\subsubsection{Physics of Contemporary Challenges}
\corinnesays{You might want to use your paragraph structure here, rather than sub-sub sections.}

In \emph{The Physics of Contemporary Challenges} we prepare students to
apply physics concepts and physical reasoning skills to sustainable
energy issues, climate change mechanisms, space exploration and
puzzles in fundamental physics. These ``real-world'' topics are chosen
for either the societal need (energy and climate), and/or the human
need to explore (space and fundamental physics). By prioritizing
inclusion of the most engaging challenges, we aim to attract and
retain as many potential physics majors as possible.

@@

While the \emph{Challenges} course takes a more experimental/applied physics
focus, the \emph{Techniques of Theoretical Mechanics} course has a more
theoretical physics flavor. The theme of this course is the discussion
of strategies for making sense of physics problems and symbolic
problem solving. This sense-making includes coordinating and
interpreting symbolic expressions with conceptual understandings,
geometric relationships, and physical intuitions.

The \emph{Theoretical Mechanics} course is aimed at students who are taking
or have completed the last course in the introductory sequence. The
physics content of the course is advanced Newtonian mechanics,
introduction to Lagrangian and Hamiltonian techniques, and special
relativity. These topics at this stage for the students are convenient
for explicit discussion of sense-making strategies in physics because
(a) students are have recently studied problems that serve as limiting
cases for these more complex problems, (b) students at this level are
transitioning from solving problems primarily involving numbers to
problems with only symbolic parameters, and (c) sense-making as strategies 
can be discussed for approaching a problem, evaluating
answers, and refining intuitions about relativistic and other
unfamiliar situations. For example, we teach students how to use
spacetime diagrams to develop a story about a relativistic situation
and how to use hyperbola trigonometry on these diagrams to perform Lorentz
transformations that can be checked against the results of algebraic
Lorentz transformations.  The sense-making goals of the course are on
an equal footing with the physics goals, and sense-making is integrated
explicitly in all aspects of the course: exams, homework and during
in-class activities. Our aim is that students will develop
sense-making skills that will improve their learning in advanced
courses and will be valued by their upper-division course instructors,
research advisors, and future employers.

@@

\section{Summary}
We have developed a significant change to the Paradigms
curriculum.  This change focuses on the first two big ideas underlying
the Paradigms project: (1) close attention to content ordering, and (2)
developing a consensus and understanding of the curriculum among our
faculty members.  Our commitment to using active engagement in our
upper-division curriculum remains unchanged.  While the specific
content ordering we developed may be interesting, the \emph{process} by
which we reached it and developed a faculty consensus is at the
essence of what makes the Paradigms in Physics program distinctive.
Emily van Zee, a researcher with experience in ..., 
\corinnesays{Emily, please add a short description of yourself} 
has completed a retrospective study of the process we used to develop the 
original Paradigms program and we have used her results extensively in 
designing and implementing the Paradigms~2.0 process.  She has continued 
to observe, study, and document our work as we have begun implementing 
the revised curriculum. 
\corinnesays{David:  Add a citation to http://physics.oregonstate.edu/portfolioswiki/toolkit:start}
The process of developing faculty understanding of the Paradigms is
ongoing, as we are having professors new to the department shadow
experienced faculty as they teach \emph{Paradigm} course, prior to teaching
the same course themselves.
